working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-02 Manuscript_draft/Manuscript_draft.Rmd
edits
effect sizes for the different species added

@@

**Figure S1**. Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae. All the species were crossed with a species of the other two families (N=3). To prepare these ratios all the pollen grains on the stigma were counted.

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="Effect sizes for the 10 different species. The different families appear with different colours, when a species was focal was coloured differently from its family."}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

#SOME
load("effect_size_species/some_effect_size.RData")
p1<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")

#SOLY
load("effect_size_species/soly_effect_size.RData")
pp2<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "B)")

#SIAL
load("effect_size_species/sial_effect_size.RData")
p3<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "C)")

#PEIN
load("effect_size_species/pein_effect_size.RData")
p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "D)")

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p5<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "E)")

#IPAQ
load("effect_size_species/ipaq_effect_size.RData")
p6<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "F)")

#ERSA
load("effect_size_species/ersa_effect_size.RData")
p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")

#CAAN
load("effect_size_species/caan_effect_size.RData")
p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")

#BRRA
load("effect_size_species/brra_effect_size.RData")
p9<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "I)")

#BROL
load("effect_size_species/brol_effect_size.RData")
p10<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "J)")

 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()
 grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))

@@

**Figure S1**. Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with species of the other two families (N=3). To prepare these ratios all the pollen grains on the stigma were counted.

### 2019-03-02 Manuscript_draft/Manuscript_draft.tex
edits
effect sizes for the different species added

@@

\textbf{Figure S1}. Pollen ratios separated by family A) Brassicaceae,
B) Solanaceae, C) Convolvulaceae. All the species were crossed with a
species of the other two families (N=3). To prepare these ratios all the
pollen grains on the stigma were counted.

\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\includegraphics{output/figures/unnamed-chunk-5-2.pdf}
\includegraphics{output/figures/unnamed-chunk-5-3.pdf}

>>>>

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

@@

\textbf{Figure S1}. Pollen ratios separated by family A) Brassicaceae,
B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with
species of the other two families (N=3). To prepare these ratios all the
pollen grains on the stigma were counted.

\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
\includegraphics{output/figures/unnamed-chunk-6-2.pdf}
\includegraphics{output/figures/unnamed-chunk-6-3.pdf}
